Throughput Prediction on 60 GHz Devices for Latency Sensitive Applications

### 2021-01-21 paper.tex
changes

Applications have a diverse requirement on the timescale of throughput prediction. VR applications for example, need to predict the throughput in the window of the next tens of milliseconds. On the other end of the spectrum, video streaming applications usually fetch video chunks of several seconds in length and therefore need to predict the average throughput in the window of the next few seconds. We are interested in the throughput predictability over 802.11ad at all these timescales and hence, we experiment with representative timescales of 10 ms, 20 ms, 40 ms, 100 ms, 200 ms, 400 ms, 1000 ms, and 2000 ms.

>>>>

Applications have a diverse requirement on the timescale of throughput prediction. VR applications for example, need to predict the throughput in the window of the next tens of milliseconds. On the other end of the spectrum, video streaming applications usually fetch video chunks of several seconds in length and therefore need to predict the average throughput in the window of the next few seconds. We are interested in the throughput predictability over 802.11ad at all these timescales, and hence we experiment with representative timescales of 10 ms, 20 ms, 40 ms, 100 ms, 200 ms, 400 ms, 1000 ms, and 2000 ms.
